### 2022-09-26 README.Rmd
weight checking
actions!

<!-- badges: start -->
<!-- badges: end -->

@@

>>>>

<!-- badges: start -->
[![Codecov test coverage](https://codecov.io/gh/jhs-hwg/nhanes-shiny-bp/branch/main/graph/badge.svg)](https://app.codecov.io/gh/jhs-hwg/nhanes-shiny-bp?branch=main)
[![R-CMD-check](https://github.com/jhs-hwg/nhanes-shiny-bp/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jhs-hwg/nhanes-shiny-bp/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

@@

## Weights

if counts are requested, we re-calibrate weights.
